`r glue::glue('inferCNV results for {params$library_id}')`

### 2025-04-25 analyses/infercnv-consensus-cell-type/template-notebooks/ewings-infercnv-results.Rmd

ggplot(cluster_size_df) + 
  aes(x = cluster_size, y = total_cnv_per_cell) +
  geom_point() + 
  facet_wrap(vars(normal_reference)) + 
  geom_smooth(method = "lm")

```

>>>>

ggplot(cluster_size_df) +
  aes(x = cluster_size, y = total_cnv_per_cell) +
  geom_point() +
  facet_wrap(vars(normal_reference)) +
  geom_smooth(method = "lm")
```
